First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2019-11-11 MY_PUBLICATIONS/PRL/body.tex
updated PRL

\indent The event selection criteria for the hydrogen and deuteron data was determined by making 1) standard cuts on the spectrometer momentum fraction ($\delta$) to select a region in which the reconstruction optics

@@

\indent The experimental data yield was normalized by the accumulated charge and corrected for tracking efficiencies, total live time, proton absorption and target boiling factors.
For $^{1}H(e,e'p)$, the corrected data yield was compared against SIMC using P. Bosted's proton form factor parametrization\cite{PhysRevC.51.409} to check the spectrometer acceptance
model. The data to SIMC yield ratio was determined to be 1.0 within uncertainty, and there was no need to include an overall hydrogen normalization factor. For the $^{2}H(e,e'p)$ data,
the theoretical cross section calculation from J.M. Laget using the Paris potential was incorporated into SIMC as a subroutine. The events generated
over phase space were weighted by the theoretical cross sections using either the PWIA or FSI models and were compared to the corrected data yield for the 80 MeV setting. Variations
of up to $\sim 20 \%$ for recoil momentum up to $\sim$ 250 MeV/c were observed which are typical for this setting. The 80 MeV data was also checked for reproducibility against the Hall A data
at this setting. This agreement gives us confidence on the measurements made at higher missing momentum setting for which no data exists. \\
\indent The experimental sections were determined by dividing the normalized data yield by the phase space over the spectrometers acceptances generated in SIMC. The data was radiatively corrected
by multiplying measured cross sections by the ratio of the SIMC yield (using the Paris potential, FSI model) without and with radiative effects for each bin in ($\theta_{nq}, p_{r}$).
The data was also bin-centered corrected by multiplying the radiative corrected cross sections by the ratio of theoretical cross section at the averaged kinematics to the average SIMC model
cross sections at the bin-centered value in ($\theta_{nq}, p_{r}$). The theoretical cross sections were determined external to SIMC using J.M. Laget's calculations at the averaged kinematics.\\

@@

\caption{\label{fig:fig1} The ratio R($p_{r}$) = $\sigma_{exp}/\sigma_{PWIA}$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
                          The dashed reference (magenta) line refers to CD-Bonn PWIA for which the data and all models are divided. }

@@

\indent The systematic uncertainties on the measured cross sections are separated in two categories: 1) normalization and 2) kinematic uncertainties. The normalization uncertainties on
the  $^{2}H(e,e'p)n$ cross section were determined to be: tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
for an overall normalization uncertainty of $3.7 \%$ added in quadrature. \\
\indent The kinematic uncertainties were determined point-to-point for ($\theta_{nq}, p_{r}$) bins for each data set independently, and added in quadrature for overlapping $p_{r}$ bins
of different data sets. The variations of the cross section with spectrometer kinematics in beam energy, electron angle and momentum and proton angle were determined from Laget PWIA model and the uncertainties
in the kinematic variables were determined from a fit to the $^{1}H(e,e'p)$ elastic data.
%For $\theta_{nq}=$ 35, 45 and 75 deg the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{r}\leq1.01$ GeV/c.
\indent The $^{2}H(e,e'p)n$ reduced cross sections for each data set were determined within the PWIA by:
\sigma_{red} \equiv \frac{\sigma_{exp}}{Kf_{rec}\sigma_{cc1}}
where $\sigma_{exp}$ is the 5-fold experimental (or model) cross section, $K$ is a kinematical factor, $f_{rec}$ is a the recoil factor that arises from the
integration over missing energy and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton offshell cross section.
In the PWIA, $\sigma_{red}$ is interpreted as the momentum distributions inside the deuteron where most of the kinematical dependencies that arise from the
cross section have been factored out. \\
\indent In Figure \ref{fig:fig1}, the ratio of the experimental to the PWIA reduced cross sections is plotted against neutron recoil momentum, $p_{r}$.

>>>>

\indent The event selection criteria was done exactly the same for the hydrogen and deuteron data. The criteria was determined by making 1) standard cuts on the spectrometer momentum fraction ($\delta$) to select a region in which the reconstruction optics

@@

\indent The experimental data yield was normalized by the total charge and corrected for tracking efficiencies, total live time, proton absorption and target boiling factors.
For $^{1}H(e,e'p)$, the corrected data yield was compared to SIMC using P. Bosted's proton form factor parametrization\cite{PhysRevC.51.409} to check the spectrometer acceptance
model. The data to SIMC yield ratio integrated over invariant mass $W$ was determined to be unity, so there was no need to include an overall hydrogen normalization factor. For the $^{2}H(e,e'p)n$ data,
the measured cross sections were compared to the model cross sections (incorporated as a SIMC subroutine) from calculations by J.M. Laget using the Paris potential. Variations
of up to $\sim 20 \%$ for recoil momenta up to $\sim$ 250 MeV/c were observed which are typical for this setting using the Paris potential. The 80 MeV data was also checked for reproducibility against the Hall A data.
This agreement gives us confidence on the measurements made at higher missing momentum setting for which no data exists. \\
\indent The systematic uncertainties on the measured cross sections were determined from 1) normalization and 2) kinematic uncertainties. The individual contributions from normalization uncertainties
were determined to be: tracking efficiencies ($0.40 \%$-HMS, $0.59 \%$-SHMS ), target boiling ($0.39 \%$), total live time ($3.0 \%$) and total charge ($2.0\%$)
for an overall normalization uncertainty added in quadrature of $3.7 \%$. \\
\indent The kinematic uncertainties were determined point-to-point in ($\theta_{nq}, p_{r}$) bins for each data set independently, and added in quadrature for overlapping $p_{r}$ bins
of different data sets. For $\theta_{nq}=$ 35, 45 and 75 deg (presented on this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{r}\leq1.01$ GeV/c.
\indent The data was radiatively corrected for each bin in ($\theta_{nq}, p_{r}$) by multiplying measured cross sections to the ratio of the SIMC yield without and with radiative effects. Bin-centering
corrections were also applied by multiplying the radiative corrected cross sections to the ratio of theoretical cross sections (external to SIMC) to the average cross sections calculated from SIMC.
The theoretical calculations used in the bin-centering corrections were done by J.M. Laget using the Paris potential. \\
\indent Both experimental and theoretical reduced cross sections were extracted from the measured (or model) cross sections for each data of set independently and were averaged for overlapping bins in $p_{r}$,
where the reduced cross sections are defined as follows:
\sigma_{red} \equiv \frac{\sigma_{exp(th)}}{Kf_{rec}\sigma_{cc1}}
where $\sigma_{exp(th)}$ is the 5-fold experimental (or theoretical) differential cross section, $K$ is a kinematical factor, $f_{rec}$ is a the recoil factor that arises from the
integration over missing energy and $\sigma_{cc1}$ is the de Forest\cite{DEFOREST1983} electron-proton offshell cross section calculated from P. Bosted's form factor parametrization \cite{PhysRevC.51.409}.
Only within the PWIA, $\sigma_{red}$ can be interpreted as the proton momentum distribution inside the deuteron where most of the kinematical dependencies that arise from the
cross section have been factored out by $\sigma_{cc1}$, leaving only a dependency on $p_{r}$. \\

@@

\caption{The ratio R($p_{r}$) = $\sigma_{red}$/n$(p_{r})$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
                              The dashed reference (magenta) line refers to CD-Bonn momentum distribution (n$(p_{r})$) by which the data and all models are divided. }
\label{fig:fig1}

@@

\indent To quantify by how much and to what extent the data agrees with theory, the ratio of the experimental (or theoretical) reduced cross sections ($\sigma_{red}$)
to the deuteron momentum distributions (n$(p_{r})$) using the charge-dependent Bonn (CD-Bonn) potential is shown in Fig. \ref{fig:fig1}. The theoretical calculations for the
CD-Bonn and Argonne $v_{18}$ (AV18) potentials were performed by M. Sargsian and those for the Paris potential were done by J.M. Laget. For $p_{r}\lesssim 300$ MeV/c, the data is
in good agreement with all models for the neutron recoil angles shown in Fig. \ref{fig:fig1}. For $p_{r}\gtrsim 300$, at recoil angles $\theta_{nq} = 35^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig1]{1(a)}],
the data is best described by the CD-Bonn curves which exhibit a reduced sensitivity to FSIs and an enhanced sensitivity to the momentum distribution with a ratio R$\sim$1 for recoil momenta
up to $\sim$ 800 MeV/c before being overwhelmed by FSIs. The data, however, is sensitive to the momentum distributions only up to $p_{r}\sim$ 750 MeV/c before transitioning to other theoretical curves
with a maximal ratio of R$\sim$3 at $p_{r}\sim$940 MeV/c due to statistical limitations. For recoil angles $\theta_{nq} = 45^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig1]{1(b)}], both the data and
CD-Bonn curves show sensitivities to momentum distributions up to $p_{r}\sim$ 580 MeV/c. At $p_{r}>580$ MeV/c, FSIs become increasingly important for CD-Bonn curves, whereas the data shows
a similar behaviour as in Fig. \hyperref[fig:fig1]{1(a)} with an early rise in the ratio than predicted by the CD-Bonn FSI model. For $\theta_{nq} = 75^{o}\pm5^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}], the
onset of GEA is observed beyond $p_{r}\sim$ 300 MeV/c, with a strong angular dependence of the reduced cross sections on FSIs predicted by all models and verified by data which was statistically limited
at larger recoil angles. \\
\indent Figure \ref{fig:fig2} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum, $p_{r}$ for three angular settings at 4$\leq Q^{2} \leq$5
(GeV/c)$^{2}$. The data is compared to the results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=$ 3.5 (GeV/c)$^{2}$.  The overlay of the Hall A data (cyan) in Fig. \ref{fig:fig2}
provides a continutity to the data from this experiment in the transition region from low (80 MeV/c) to high (580, 750) MeV/c missing momentum settings in which there was no data. There is also an overall good agreement between the two experiments
in the regions in which there is an overlap in $p_{r}$. \\
\indent Below $p_{r}\sim 300$ MeV/c, both Hall A and C data agree well with all theoretical models, as FSIs and other non-cucleonic 
\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\onecolumngrid

\begin{figure}[bh!]
\includegraphics[scale=0.5]{prl_plots/PRL_plot1.pdf}
\caption{The reduced cross section $\sigma_{red}(p_{r})$ as a function of neutron recoil momentum $p_{r}$ is shown in (a)-(c) for recoil angles \\  $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively,
with a bin width of $\pm 5^{o}$. The data is compared to the previous Hall A experiment results as well as the Paris, AV18 and CD-Bonn theoretical reduced cross sections.}
\label{fig:fig2}
\end{figure}
\newpage
\twocolumngrid
%\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
